### 2013-05-16 draft.tex
edited Eprobe and bulk trace metal sections to explain why we did them

Electron backscatter diffraction (EBSD) provides an independent measure of recrystallization by mapping the orientation of calcite crystals in a thin section. This allows more detailed characterization of calcite fabrics than is possible using optical microscopy, and in the case of brachiopods, comparison to pristine modern examples \citep{PerezHuerta2007}. The thin sections were analyzed using a Zeiss 1550VP Field Emission Scanning Electron Microscrope (SEM) under variable pressure vacuum, with an electron high tension of 20 kV. The stage was tilted 70$^{\circ}$. The AZtec program was used in $4\times4$ binning mode, with frame averaging over one frame and a step size of 2 $\mu$m for the rugose coral and 1.2 $\mu$m for the brachiopod. The electron beam interacts with the crystal and is diffracted in a characteristic pattern for calcite. The diffracted beam then interacts with the EBSD detector, depdending on the orientation of the calcite crystal. The data were analyzed using software from Oxford instruments.

@@

The same thin sections as above were first coated with a layer of carbon 15 nm thick, and then analyzed with wavelength-dispersive spectroscopy using the JEOL JXA-8200 Electron Probe Micro-analyzer. Using the JEOL map analysis program, the beam was calibrated on crystals of dolomite, siderite, strontianite and rhodochrosite. Qualitative maps of Ca, Mg, Fe, Sr and Mn concentration were made using a current of 200 nAmps, voltage of 15 kV, and a counting time of 80 milliseconds per pixel. Quantitative spot measurements were made using the JEOL quantitiative analysis program.

@@

Between 1 and 5 milligrams of each powdered sample were dissolved in a known volume of 4\% nitric acid (HNO$_3$). Standards were prepared from standard solutions of Sr, Mn and Fe with the same concentration of Ca and HNO$_3$ as the sample solutions to minimize matrix effects. Solutions were sampled using a Cetac ASX 260 autosampler, aspirated into the Ar plasma using a peristaltic pump, and then analyzed on a Thermo Scientific iCAP 6000 series inductively-coupled plasma optical emission spectrometer (ICP-OES). Between each set of ten unknown samples, three standard solutions (10 ppb, 100 ppb, and 1 ppm) were measured. Reproducibility was on average 3\% for Fe, 2\% for Mn and 3\% for Sr.

>>>>

Electron backscatter diffraction (EBSD) provides an independent measure of recrystallization by mapping the orientation of calcite crystals in a thin section. This allows more detailed characterization of calcite fabrics than is possible using optical microscopy, and in the case of brachiopods, comparison to pristine modern examples \citep{PerezHuerta2007}. Two thin sections, one rugose coral and one brachiopod, were analyzed using a Zeiss 1550VP Field Emission Scanning Electron Microscrope (SEM) under variable pressure vacuum, with an electron high tension of 20 kV. The stage was tilted 70$^{\circ}$. The AZtec program was used in $4\times4$ binning mode, with frame averaging over one frame and a step size of 2 $\mu$m for the rugose coral and 1.2 $\mu$m for the brachiopod. The electron beam interacts with the crystal and is diffracted in a characteristic pattern for calcite. The diffracted beam then interacts with the EBSD detector, depdending on the orientation of the calcite crystal. The data were analyzed using software from Oxford instruments.

@@

The use of wavelength-dispersive spectroscopy in combination with optical microscopy and EBSD allows characterization of the trace metal contents of specific calcite textures. By comparing the trace metal concentrations of primary textures to those of diagenetic textures, we can identify the trace metal signature of diagenetic alteration in our sample set. The same thin sections as above were coated with a layer of carbon 15 nm thick, and then analyzed with wavelength-dispersive spectroscopy using the JEOL JXA-8200 Electron Probe Micro-analyzer. Using the JEOL map analysis program, the beam was calibrated on crystals of dolomite, siderite, strontianite and rhodochrosite. Qualitative maps of Ca, Mg, Fe, Sr and Mn concentration were made using a current of 200 nAmps, voltage of 15 kV, and a counting time of 80 milliseconds per pixel. Quantitative spot measurements were made using the JEOL quantitiative analysis program.

@@

Although we attempted to sample only well-preserved skeletal material for the carbonate clumped isotope measurements, the large mass of material required makes it very difficult to avoid including small amounts of other phases. The trace metal concentrations of bulk samples can be used as an indicator of the amount of sediment and recrystallized material included in the sample \citep{Azmy1998,Brand1980,Brand2012,Came2007,Finnegan2011,Shields2003}. To measure bulk trace metal concentrations, between 1 and 5 milligrams of each powdered sample were dissolved in a known volume of 4\% nitric acid (HNO$_3$). Standards were prepared from standard solutions of Sr, Mn and Fe with the same concentration of Ca and HNO$_3$ as the sample solutions to minimize matrix effects. Solutions were sampled using a Cetac ASX 260 autosampler, aspirated into the Ar plasma using a peristaltic pump, and then analyzed on a Thermo Scientific iCAP 6000 series inductively-coupled plasma optical emission spectrometer (ICP-OES). Between each set of ten unknown samples, three standard solutions (10 ppb, 100 ppb, and 1 ppm) were measured. Reproducibility was on average 3\% for Fe, 2\% for Mn and 3\% for Sr.
